MONID

### 2023-09-12 Presentation/presentation.tex
update

>>>>

\begin{frame}
    \frametitle{Performances}
    MONID was evaluated against smurf, port-sweep, and password-guessing attacks using DARPA Intrusion Detection Evaluation dataset in offline mode, detecting 5 password-guess attacks and 2 port-sweep attacks.
    \begin{figure}[!htb]
        \begin{center}
            \begin{minipage}{0.45\textwidth}
                \centering
                \includegraphics[width=\linewidth]{images/graph 1.png}
                \caption{Performances overhead of Port-Sweep attacks.}\label{graph1}
            \end{minipage}
            \hfill
            \begin{minipage}{0.45\textwidth}
                \centering
                \includegraphics[width=\linewidth]{images/graph 2.png}
                \caption{Performances overhead of Password-Guessing attacks.}\label{graph2}
            \end{minipage}
        \end{center}
    \end{figure}
